\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-09-01 Paper/Paper.tex
change layout
Complete refining acc and loss graph

	\section*{Abstract}

	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanics, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.

	\section{Background}
	Ocular diseases can be diagnosed through various methods, including using optical coherence tomography (OCT) and color fundus images. Ophthalmologists usually identify ocular abnormalities to deduce the disease. Traditionally, the diagnosis primarily depends on the professional experience and knowledge of the ophthalmologists, which may result in high misdiagnosis rate and under-utilization of medical data. With the widespread application of artificial intelligence (AI), deep learning (DL) has made great contributions in providing support to patients in remote areas by sharing expert knowledge \autocite{Ichhpujani_Thakur_2021}. By leveraging DL, researchers have developed auxiliary diagnosis programs to help ophthalmologists in the process. Many studies use convolutional neural networks (CNN) to analyze ocular images. Some commonly used CNNs are VGG, ResNet, and Inception \autocite{daich2023artificial}. And for segmenting images and finding abnormalities, U-net is widely used \autocite{Ronneberger_Fischer_Brox_2015}. With regards to training CNNs, most studies use transferred learning, which consists of three steps: learning, fine-tuning, and validation.

@@

@@

@@

	For both OCT and Fundus Models, we trained 4 commonly used CNNs: ResNet152, ResNet50, ResNet18, and VGG16. The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
		\caption{AO train}
		\vspace{0.3cm}
		\label{fig:AO_train}
	\end{figure}

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
		\caption{AF train}
		\vspace{0.3cm}
		\label{fig:AF_train}
	\end{figure}

>>>>

	\vspace{-0.2cm}
	\hrule
	\vspace{-0.1cm}
	\section*{Abstract}
	\hrule
	\vspace{0.4cm}
	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanics, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.
	\vspace{0.4cm}
	\hrule
	\vspace{1cm}

	\begin{multicols}{2}
	\section{Background}
	Ocular diseases can be diagnosed through various methods, including using optical coherence tomography (OCT) and color fundus images. Ophthalmologists usually identify ocular abnormalities to deduce the disease. Traditionally, the diagnosis primarily depends on the professional experience and knowledge of the ophthalmologists, which may result in high misdiagnosis rate and under-utilization of medical data. With the widespread application of artificial intelligence (AI), deep learning (DL) has made great contributions in providing support to patients in remote areas by sharing expert knowledge \autocite{Ichhpujani_Thakur_2021}. By leveraging DL, researchers have developed auxiliary diagnosis programs to help ophthalmologists in the process. Many studies use convolutional neural networks (CNN) to analyze ocular images. Some commonly used CNNs are VGG, ResNet, and Inception \autocite{daich2023artificial}. And for segmenting images and finding abnormalities, U-net is widely used \autocite{Ronneberger_Fischer_Brox_2015}. With regards to training CNNs, most studies use transferred learning, which consists of three steps: learning, fine-tuning, and validation.

@@

	\end{multicols}

@@

	\begin{multicols}{2}

@@

	For both OCT and Fundus Models, we trained 4 commonly used CNNs: ResNet152, ResNet50, ResNet18, and VGG16. The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:A_train}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/abnormity_OCT_loss_and_acc.pdf}
	\end{figure}
	\begin{figure}[htbp]
		\centering
		\vspace{-1cm}
		\includegraphics[width=\linewidth]{Figs/abnormity_Fundus_loss_and_acc.pdf}
		\caption{Abnormity training}
		\vspace{0.3cm}
		\label{fig:A_train}
	\end{figure}
